A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-13 analysis/paper/paper.Rmd
align up the text in Table 2 and adjust cell widths

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-Euorpean", median_pre = "pre-Euorpean", 
                    `2.5%_pre` = "pre-Euorpean", `97.5%_pre` = "pre-Euorpean",
                    mean_post = "post-Euorpean", median_post = "post-Euorpean", 
                    `2.5%_post` = "post-Euorpean", `97.5%_post` = "post-Euorpean") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  set_caption("Estimated posterior means, medians, and 95% credible intervals for each network parameter of two models.") 
ft
```

>>>>

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-Euorpean", median_pre = "pre-Euorpean", 
                    `2.5%_pre` = "pre-Euorpean", `97.5%_pre` = "pre-Euorpean",
                    mean_post = "post-Euorpean", median_post = "post-Euorpean", 
                    `2.5%_post` = "post-Euorpean", `97.5%_post` = "post-Euorpean") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  align(j = 2:9, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  width(j = ~ parameter, width = 1.3) %>% 
  set_caption("Estimated posterior means, medians, and 95% credible intervals for each network parameter of two models.")
ft
```
